---
title: "Midpoint Deliverable"
author: "Aviraj Singh, Brandon Wong, EJ Velasco, Tony Fei"
date: "18/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("first_chart.R")

```

## Introduction
For our project, our domain of interest is to observe the transition of standardized tests being a requirement for admission by universities. Specifically, we have narrowed our scope to analyze the relationship between average SAT scores and their relationship to income across cities in California. As an objective of our project, we would like to uncover some of the discepencies from area to area and how it affects students' score. Thus, findings from our report will reveal whether standardized test are a true reflection of a student's capabilities. The source of the data is from [California Department Of Education](https://www.cde.ca.gov/ds/sp/ai/) and [IRS website](https://www.irs.gov/statistics/soi-tax-stats-individual-income-tax-statistics-2017-zip-code-data-soi). 

## Summary Information


## Summary Table


## First Visualization

The purpose of this visualization is to highlight the potential relationship between geographical locations and the average SAT performace. Using map visualization, we can get a better insight on location vs. SAT performance. Here is the visualization:

```{r, echo=F, warning=F}
map_gen()
```
From the map visualization we can see there seems to be a higher percentage of student passing the performance benchmark near San Francisco and Sacramento than other places. Student near Fresno seems to have lower performance than others. 


## Second Visualization
```{r, echo = FALSE}
ggplotly(plot_ca)
```

## Third Visualization

