---
title: "Midpoint Deliverable"
author: "Aviraj Singh, Brandon Wong, EJ Velasco, Tony Fei"
date: "18/05/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("summary_info.R")
source("summary_table.R")
source("first_chart.R")
library("knitr")
<<<<<<< HEAD
```

## Introduction
For our project, our domain of interest is to observe the transition of standardized tests being a requirement for admission by universities. Specifically, we have narrowed our scope to analyze the relationship between average SAT scores and their relationship to income across cities in California. As an objective of our project, we would like to uncover some of the discepencies from area to area and how it affects students' score. Thus, findings from our report will reveal whether standardized test are a true reflection of a student's capabilities. The source of the data is from [California Department Of Education](https://www.cde.ca.gov/ds/sp/ai/) and [IRS website](https://www.irs.gov/statistics/soi-tax-stats-individual-income-tax-statistics-2017-zip-code-data-soi). 



## Purpose of the Project

>>>>>>> 4772b320236dea4e863e4033a87c5e2a3e851d21

## Summary Information

The summary includes some interesting analysis of how household income
corelates to a student's total SAT score. Based on our data, the mean
and median household income for California is 
`r summary_information$mean_household_income` and `r summary_information$median_household_income`
respectively.The average SAT score for kids in below average income
household was `r summary_information$avg_score_below_mean_inc` and for kids
in above average income household was 
`r summary_information$avg_score_above_mean_inc`.The zip code with the highest
median household income was `r summary_information$zip_with_max_income`.

## Summary Table

The summary table portrays how total sat score and mean household income
are different for different areas(Zip code) in California.

```{r kable_example, echo = FALSE, warning = FALSE}
kable(summary_table)
```

From the table, we can clearly observe that zip codes in the beggining 
of the list are the areas with way less than average household income
and low sat scores whereas zip codes towards the end of the list are 
the areas with way more average household incomes and high sat scores.

## First Visualization

The purpose of this visualization is to highlight the potential relationship
between geographical locations and the average SAT performace. Using map
visualization, we can get a better insight on location vs. SAT performance.
Here is the visualization:

```{r, echo=F, warning=F}
map_gen()
```

From the map visualization we can see there seems to be a higher percentage
of student passing the performance benchmark near San Francisco and Sacramento
than other places. Student near Fresno seems to have lower performance than 
others. 


## Second Visualization
```{r, echo = FALSE}
ggplotly(plot_ca)
```

## Third Visualization

